### 2021-06-09 rebuttal.tex

We thank the reviewers for their thorough reading  and interesting comments.
We understand that althought the paper is relevant, some parts should be clarified. We would be happy to be shepperded if reviewers believe it is relevant.

Below, we reply to each remark in more detail.

- R1.1. "forwarding the best known partition"  consists in transmitting the best location where to get the replica.
It could be more formally defined.

- R1.2.  We agree ``Theorem'' is more appropriate than ``Corollary''. Regarding the proof, additional information would be given (under shepperding).

- R1.3. Regarding Theorem 2, we chose to list all cases to help understand the algorithm.
Every Add/Del operation creates a small subset of events that depends on its nature,
and the neighbors' history. This allows us to perform a neighbor-to-neighbor analysis of cases and avoid any combinatorial explosion.

- R2.1. Our objective is to introduce AS-cast and its properties in a generic manner. 
Hence, experiments focus on evaluating the correctness/costs of our protocol.
As stated in Conclusion, we plan to assess the use of AS-cast in IPFS distributed storage. This study would clarify its tradeoff depending on object size, update frequency, etc.

- R2.2. AS-cast is more efficient than CDN: it allows (i) retrieving the closest location eventually and (ii) partitioning the infrastructure dynamically according to the creation/removal of replicas. Contrarily, CDN relies on a static partitioning of the infrastructure: nodes get replicas from a subset of specific nodes and for all objects. A node may contact a peer of the CDN infrastructure while a replica may exist only one hop away (replicated by one of its neighbors). 
AS-cast natively deals with such cases as any node can serve a replica.

- R2.3.  The scalability issue related to the management of thousands of 
objects should be addressed. As stated in Conclusion, we propose to leverage the
hierarchical properties of inter-autonomous systems to avoid flooding uninterested nodes. 
However, this increases the complexity to prove that our protocol still converge.

- R3.1. In addition to  R2.3, we confirm that partitioning is per-object.
Yet, it would be straightforward indeed to mutualize traffic, e.g., using dedicated propagation windows to consolidate control messages together.

- R3.2. AS-cast does not handle replication strategies. If it exists only one source and it crashes, this reference eventually disappears from the system. AS-cast reacts similarly to crashes and departures of sources (see Algorithm 3 Line 4) to update the best partition known by impacted nodes.

- R3.3. We do not  address the issue of content mutability.
From our viewpoint, this aspect is application-dependent. For instance, mutability could be provided by versioning as done in IPFS, BlobSeer, etc.

- R3.4. Regarding the experiments remarks, please, refer to R2.2.

- R3.5. Several approaches tackle the indexation problem in NDN. We were unaware of NDNS and agree to add it in Related Work.

- R3.6. Although network topologies include triangular inequalities,  they do not endanger the AS-CAST correctness (AS-CAST relies on the shortest distance between vertices).

### 2021-09-01 RR-9418.tex
cosmetic + number

\RRNo{XXXX}
\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  \thanksref{aff1}
  \and
  Alexandre Van Kempen
  \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation de contenu décentralisée au niveau du Edge} %% titre français long
\titlehead{\RRtitle{} } %% titre français court
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

@@

\RRmotcle{Indexation de contenu, partitionnement logique, algorithme décentralisé}
\RRkeyword{Content indexing, logical partitioning, decentralized algorithm}

@@

\makeRR
\RRNo{XXXX}

>>>>

\RRNo{9418}
\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  %%  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  %% \thanksref{aff1}
  \and
  Alexandre Van Kempen
  %% \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long
\titlehead{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français court
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

@@

\RRmotcle{Indexation de contenu, partitionnement logique, algorithme décentralisé, Edge}
\RRkeyword{Content indexing, logical partitioning, decentralized algorithm, Edge}

@@

\makeRR
\RRNo{9418}

### 2021-09-01 input/experiments.tex
spacing
cosmetic + number

\begin{figure}
  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of consistent partitioning
    using \NAME.}
  %% \caption{\label{fig:complexity}Cumulative average number of messages
  %%   per process in a network comprising 10k processes; along with the
  %%   duration before reaching consistent partitioning after adding or
  %%   removing a partition, totaling 100 new partition then removed.}
\end{figure}

@@

\begin{figure}
  \centering\includegraphics[width=0.99\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
\end{figure}

@@

\noindent Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ ms delay corresponding to the link latency, the
cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

>>>>

\begin{figure}
  \centering\includegraphics[width=0.8\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of consistent partitioning
    using \NAME.}
  %% \caption{\label{fig:complexity}Cumulative average number of messages
  %%   per process in a network comprising 10k processes; along with the
  %%   duration before reaching consistent partitioning after adding or
  %%   removing a partition, totaling 100 new partition then removed.}
\end{figure}

@@

\begin{figure}
  \centering\includegraphics[width=0.8\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters.}
\end{figure}

@@

\noindent Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ milliseconds delay corresponding to the link latency, the
cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

### 2021-09-01 input/figproblem.tex
minors
cosmetic + number

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both \Process~$a$ and
      \Process~$d$ add then delete their partition. For the recall,
      $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
      3$.]{\input{input/figproblemA.tex}}
    \hspace{5pt} \subfloat[Part B][\label{fig:problemB}\Process~$b$
      delivers and forwards the $\alpha$ message about $P_a$ while
      \Process~$c$ delivers and forwards both $\alpha$ and $\delta$
      messages about $P_d$.]  {\input{input/figproblemB.tex}}
    \hspace{5pt} \subfloat[Part C][\label{fig:problemC}\Process~$b$
      already blocks the propagation of $\delta_a$ despite it
      propagated $\alpha_a$ before. \Process~$c$ and \Process~$d$ do not
      deliver $\alpha_d$, for they already deleted
      it before.]{\input{input/figproblemC.tex}}
    \hspace{5pt} \subfloat[Part D][\label{fig:problemD}\Processes
      discard remaining messages. Since \Process~$b$ cannot deliver
      $\delta_a$, $c$ and $d$ remain in the deleted partition
      $P_a$.]{\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Naive propagation of $\alpha$ and
    $\delta$ messages is insufficient to guarantee consistent partitioning.}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both \Process~$a$ and
      \Process~$d$ add then delete their partition. For the recall,
      $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
      3$.]{\input{input/figproblemA.tex}}
    \hspace{1pt}
    \subfloat[Part B][\label{fig:problemB}\Process~$b$
      delivers and forwards the $\alpha$ message about $P_a$ while
      \Process~$c$ delivers and forwards both $\alpha$ and $\delta$
      messages about $P_d$.]  {\input{input/figproblemB.tex}}
    \hspace{1pt}
    \subfloat[Part C][\label{fig:problemC}\Process~$b$
      already blocks the propagation of $\delta_a$ despite it
      propagated $\alpha_a$ before. \Process~$c$ does not deliver
      $\alpha_d$, for it already deleted it
      before.]{\input{input/figproblemC.tex}}
    \hspace{1pt}
    \subfloat[Part D][\label{fig:problemD}\Processes
      discard remaining messages. Since \Process~$b$ cannot deliver
      $\delta_a$, $c$ and $d$ remain in the deleted partition
      $P_a$.]{\input{input/figproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Naive propagation of $\alpha$ and
    $\delta$ messages is insufficient to guarantee consistent partitioning.}
\end{figure*}

### 2021-09-01 input/proposal.tex
cosmetic + number

\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
  When \Process~$x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct \process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on the \underline{s}tate $\sigma$ of
  each \process, the \underline{m}etadata $\mu$ piggybacked by each
  message, and a \underline{p}redicate $\phi$ verified from \process to
  \process: {\small{$b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$}}.
\end{definition}

@@

\begin{definition}[\label{def:partitioning}Partitioning]
  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
  the \underline{p}artition including at least \Process~$s$, each
  \process belongs to at most one partition \smash{\small$\forall p,q \in V, \forall
  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
  \vee s_1 = s_2$}, and there exists at least one path $\pi_{ps}$ of
  \processes that belong to this partition $\forall q \in \pi_{ps}: q
  \in P_s$.
\end{definition}

>>>>

\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
  When \Process~$x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct \process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on the \underline{s}tate $\sigma$ of
  each \process, the \underline{m}etadata $\mu$ piggybacked by each
  message, and a \underline{p}redicate $\phi$ verified from \process to
  \process: {$b_x(m) \wedge r_y(m) \implies \exists \pi_{xy}: \forall z
  \in \pi_{xy}, \phi(\mu_z, \sigma_z)$}.
\end{definition}

@@

\begin{definition}[\label{def:partitioning}Partitioning]
  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
  the \underline{p}artition including at least \Process~$s$, each
  \process belongs to at most one partition \smash{$\forall p,q \in V, \forall
  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies$} \smash{$p \neq q
  \vee s_1 = s_2$}, and there exists at least one path $\pi_{ps}$ of
  \processes that belong to this partition $\forall q \in \pi_{ps}: q
  \in P_s$.
\end{definition}
